\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-21 papers/jss/article.Rnw
Switch order of mapreduce/web services sections in the last paragraph of the intro since we've moved the order of them in the text.
For a figure in the mapreduce example section, make the histogram
more vertically compact to not waste so much space.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@799 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

This paper describes an R interface to Protocol Buffer, 
and is organized as follows. Section~\ref{sec:protobuf}
provides a general overview of Protocol Buffers.
Section~\ref{sec:rprotobuf-basic} describes the interactive R interface
provided by \CRANpkg{RProtoBuf} and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
describes the implementation details of the main S4 classes making up this
package.  Section~\ref{sec:types} describes the challenges of type coercion
between R and other languages.  Section~\ref{sec:evaluation} introduces a
general R language schema for serializing arbitrary R objects and evaluates
it against R's built-in serialization.  Sections~\ref{sec:opencpu}
and \ref{sec:mapreduce} provide real-world use cases of \CRANpkg{RProtoBuf}
in web service and MapReduce environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

<<echo=FALSE,fig=TRUE>>=
require(RProtoBuf)
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("hist.pb")
plot(as.histogram(hist))
@

>>>>

This paper describes an R interface to Protocol Buffer, 
and is organized as follows. Section~\ref{sec:protobuf}
provides a general overview of Protocol Buffers.
Section~\ref{sec:rprotobuf-basic} describes the interactive R interface
provided by \CRANpkg{RProtoBuf} and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
describes the implementation details of the main S4 classes making up this
package.  Section~\ref{sec:types} describes the challenges of type coercion
between R and other languages.  Section~\ref{sec:evaluation} introduces a
general R language schema for serializing arbitrary R objects and evaluates
it against R's built-in serialization.  Sections~\ref{sec:mapreduce}
and \ref{sec:opencpu} provide real-world use cases of \CRANpkg{RProtoBuf}
in MapReduce and web service environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

<<echo=FALSE,fig=TRUE,width=8,height=4>>=
require(RProtoBuf)
require(HistogramTools)
readProtoFiles(package="HistogramTools")
hist <- HistogramTools.HistogramState$read("hist.pb")
plot(as.histogram(hist))
@
